---
title: "Statistical Inference-Exponential Distribution vs CLT"
author: "Devara Izaz Fathan"
date: "8/22/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# 1. Overview
This assignment evaluates the exponential distribution versus Central Limit Theorem. We will use rexp function to do the simulation. The values used in this asignment are lambda= 0.2 and numberofsimulation=1000. We are going to do simulation, comparing sample mean vs theoritical mean, comparing sample variance versus theoritical variance and its distribution.  

# 2. Simulation
The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. We will do 1000 simulation.

```{r, echo=FALSE}
##Load the library that will be used
library(knitr)
library(dplyr)
library(tidyverse)
library(ggplot2)

```

```{r}
lambda <- 0.2
n <- 40 #number of sample
B <- 1000 #number of simulation
set.seed(8)
## do the simulation
data_sample <- data.frame(matrix(rexp(n*B, lambda), nrow = B, ncol = n))
data_sample <- data_sample %>% mutate(mean_sample = rowMeans(data_sample)) 

```

# 3. Sample Mean VS Theoritical Mean
Based on theory, the mean for the theoritical data is 1/lambda. Here is the code:
```{r}
theoritical_mean <- 1/lambda
print(theoritical_mean)

```
Then we compute the sample mean with data_sample dataset.
```{r}
sample_mean <- mean(data_sample$mean_sample)
print(sample_mean)

```
Based on those two codes above, we have got the the theoretical mean = 5, and the sample mean = 5.018281. Those values are very close enough to each other.

```{r}
data_sample %>% ggplot(aes(mean_sample, ..density..)) + 
      geom_histogram(binwidth = 0.2, position = 'identity', col= 'black', fill='blue') +
      xlab('Sample Mean') + 
      ylab('Density') +
      ggtitle('Distribution of Sample Means') +
      geom_vline(xintercept = theoritical_mean, color='black') +
      geom_vline(xintercept = sample_mean, color= 'yellow')
      
      
```

# 4. Sample Variance versus Theoretical Variance
Based on theory, the variance for the theoretical data is sd^2/n. Here is the code:
```{r}
theoritical_variance <- (1/lambda)^2/n
print(theoritical_variance)

```
Then we compute the sample variance using data_sample dataset that we have been created.
```{r}
sample_variance <- var(data_sample$mean_sample)
print(sample_variance)

```
Based on those two codes above, we have got the theoretical variance = 0.625, and the sample variance = 0.636219

# 5. Distribution
Based on Central Limit Theorem, the distribution of the sample mean should follow this theorem. We will see the density plot here
```{r}
data_sample %>% ggplot(aes(mean_sample, ..density..)) + 
      geom_histogram(binwidth = 0.2, position = 'identity', col= 'black', fill='blue') +
      xlab('Sample Mean') + 
      ylab('Density') +
      ggtitle('Distribution of Sample Means') +
      geom_vline(xintercept = theoritical_mean, color='black') +
      geom_vline(xintercept = sample_mean, color= 'yellow') +
      geom_density(colour='darkgreen', size=1)

```

To give more evidence that the distribution sample mean occurs in Central Limit Theorem, we use qq plot function.

```{r}
mean_sample <- data_sample$mean_sample
qqnorm(mean_sample, main='Normal qq plot');qqline(mean_sample, col='3')

```




This QQ plot show a close relationship between the data sample mean and the theoritical mean. Thats why we can say that Our simulation is approximately a normal distribution.

